Algorithmic and Economic Aspects of the Internet

### 2012-12-03 report/paper.tex
Added figures to latex.
Referenced figures

\subsubsection{1 v 1} No trading occurs in this experiment. In the graphs
below, you can see the shouts made by the bots. The Shaver buyer and seller
traders tend toward the equilibrium price over time but don't manage to reach
it before the market session ends. The AA bot makes very few trades and is
always out-bid / out-asked by Shaver.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_bids.png}
\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the bids made.}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_asks.png}
\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the asks made.}
\end{figure}

\subsubsection{1 v Many} In these experiments, trading starts at around round
90. In the graphs below, we see that the Shaver bots tend towards the
equilibrium much faster than when there was only one bot; this is likely due to
there being 10 Shaver bots which are all trying to out-bid each other. When the
bids and asks converge, the Shaver bots invariably trade with themselves. Our
AA implementation is excluded from trading as it can't adjust its
aggressiveness quickly enough. Not all Shaver bots are engaged in making actual
trades at all times, the horizontal lines of bids / asks on the graphs indicate
that a Shaver bot is placing shouts at its limit price.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_bids.png}
\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the bids made.}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_asks.png}
\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the asks made.}
\end{figure}

@@

\subsubsection{Many v Many} Again, trading begins at around round 90. We see
the same pattern as we do in the previous experiment except that AA is making
more bids / asks. On this occasion we see that AA actually manages to make a
few profitable trades between rounds 90 and 140 before being swamped by the
simpler and more effective aggressiveness function of the correctly implemented
Shaver bot. These few trades are more by chance than by design; the dip in bid
price would have intersected with the poorly adapting AA bot allowing AA to
place bids that would be accepted by the seller Shaver traders.

>>>>

\subsubsection{1 v. 1} No trading occurs in this experiment. In figures 2 and 3,
you can see the shouts made by the bots. The Shaver buyer and seller traders
tend toward the equilibrium price over time but don't manage to reach it before
the market session ends. The AA bot makes very few trades and is always out-bid
/ out-asked by Shaver.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_bids.png}
\caption {1 AA versus 1 Shaver}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_asks.png}
\caption {1 AA versus 1 Shaver}
\end{figure}

\subsubsection{1 v. Many} In these experiments, trading starts at around round
90. In figures 4 and 5, we see that the Shaver bots tend towards the
equilibrium much faster than when there was only one bot; this is likely due to
there being 10 Shaver bots which are all trying to out-bid each other. When the
bids and asks converge, the Shaver bots invariably trade with themselves. Our
AA implementation is excluded from trading as it can't adjust its
aggressiveness quickly enough. Not all Shaver bots are engaged in making actual
trades at all times, the horizontal lines of bids / asks on the graphs indicate
that a Shaver bot is placing shouts at its limit price.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_bids.png}
\caption {1 AA versus 10 Shavers}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_asks.png}
\caption {1 AA versus 10 Shavers}
\end{figure}

@@

\subsubsection{Many v Many} Again, trading begins at around round 90. In figures
6 and 7, we see the same pattern as we do in the previous experiment except that
AA is making more bids / asks. On this occasion we see that AA actually manages
to make a few profitable trades between rounds 90 and 140 before being swamped
by the simpler and more effective aggressiveness function of the correctly
implemented Shaver bot. These few trades are more by chance than by design; the
dip in bid price would have intersected with the poorly adapting AA bot allowing
AA to place bids that would be accepted by the seller Shaver traders.

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA10_180_all_bids.png}
\caption {10 AAs versus 10 Shavers}
\end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA10_180_all_asks.png}
\caption {10 AAs versus 10 Shavers}
\end{figure}
